Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
add podd citation that was not converted initially

Thus, to support publicly-funded phenomics activities in Australia, the
Phenomics Ontology Driven Data repository (PODD) has been developed as a
repository for data produced by the variety of plant imaging and phenotyping
platforms available at the High Resolution Plant Phenomics Centre, as well as
for recording the contextual metadata associated with plant genotypes,
treatments and environmental conditions [13]. PODD manages the links between the
raw image files generated by plant imaging platforms, the results from analyses,
and conclusions by scientists.

>>>>

Thus, to support publicly-funded phenomics activities in Australia, the
Phenomics Ontology Driven Data repository (PODD) has been developed as a
repository for data produced by the variety of plant imaging and phenotyping
platforms available at the High Resolution Plant Phenomics Centre, as well as
for recording the contextual metadata associated with plant genotypes,
treatments and environmental conditions \cite{Li2010}. PODD manages the links between the
raw image files generated by plant imaging platforms, the results from analyses,
and conclusions by scientists.
